%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Integration Analyst } % Job title
    {Roy Hill Iron Ore} % Organization
    {Perth, Western Australia} % Location
    {Aug. 2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed,  built and supported several RESTful API services for Mobile Applications utilized within the company}
        \item {Designed and implemented a custom solution for real time Change data capture from operational databases using Java, Apache Kafka, Debezium and MySQL, provisioned and support all involved platforms}
        \item {Administer, Develop and support API, B2B and external integration services interacting with many 3rd party and internal Vendors and Applications on the SAP Netweaver Platform}
        \item {Extended and Maintained a custom Master Data Management Tool Utilizing SAP HANA, Netweaver and Fiori/UI5}
        \item {Technical Lead for Business System integration (BAU \& Greenfield Projects }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {Keepspace} % Organization
    {Perth, Australia} % Location
    {Mar. 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing static website content for onboarding of users}
        \item {Developing A visual display of a Customer’s stored items in a single page application using ReactJS }
        \item {Formulating marketing strategies and UX guidelines for the business}
      \end{cvitems}
    }

%---------------------------------------------------------

\cventry
    {Undergraduate Researcher} % Job title
    {Undergraduate Projects, Curtin CompSci Dept. w/ Curtin Psychology Dept.} % Organization
    {Perth, Australia} % Location
    {Mar. 2014 - Nov. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched Computational Methods for mapping of a Patient’s gaze to positions on a computer screen for diagnosis of medical/psychological conditions.}
        \item {Developing a software based delivery system for stimuli and recording of patient’s face in real-time using Open Source Computer Vision toolsets and C++}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
